Parameter Inference\\with Bifurcation Diagrams

### 2021-05-23 docs/article.tex
Updates from Overleaf

\subsection{Genetic Toggle Switch | \textit{in progress}}
In this section we optimise a model where the states share a Hill function relationship; these models often emerge from mass action kinetics and are used to model species concentrations. By not restricting the sign of the coefficients $a_1,a_2$ we can recover both activator and inhibitor relationships.
\begin{equation}
    \partial_t u_1 = \frac{ a_1 + (pu_2)^2} { 1 + (pu_2)^2 } - \mu_1 u_1 \quad
    \partial_t u_2 = \frac{ a_2 + (ku_1)^2} { 1 + (ku_1)^2 } - \mu_2 u_2
    \label{eq:two-state}
\end{equation}
Figure \ref{fig:two-state-optima} shows a UMAP embedding of the optimal parameter basins, represented as point clouds. 16 distinct clusters are obtained using DBSCAN. Each cluster corresponds to a kinetically different model regions that are qualitatively equivalent. See Appendix \ref{appendix:clusters} for models that represent the centroid of each cluster.

>>>>

\subsection{Genetic Toggle Switch}
In this section we optimise a model where the states share a Hill function relationship with cooperatively $n=2$; these models often emerge from mass action kinetics and are used to model species concentrations. After re-scaling the equations governing the dynamics of concentrations, the simplified equations for state $u_$ and $u_2$ become 
\begin{equation}
    \partial_t u_1 = \frac{ a_1 + (p u_2)^2}{ 1 + (p u_2)^2 } - \mu_1 u_1 \quad
    \partial_t u_2 = \frac{ a_2 + (k u_1)^2}{ 1 + (k u_1)^2 } - \mu_2 u_2
    \label{eq:two-state}
\end{equation}
where $a_k$ are 
 the  we can recover both activator and inhibitor relationships.
Figure \ref{fig:two-state-optima} shows a UMAP embedding of the optimal parameter basins, represented as point clouds. 16 distinct clusters are obtained using DBSCAN. Each cluster corresponds to a kinetically different model regions that are qualitatively equivalent. See Appendix \ref{appendix:clusters} for models that represent the centroid of each cluster.
